Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-11-09 WSSSPE4_report/WSSSPE4_report.tex
adding social science section for Stuart to write

\begin{itemize}
\item Verifying best practices \& metrics for sustainable research software [Ray Idaszak]
\item \todo{to confirm} Software Sustainability Alliance [Neil \& Jean]
\item Scientific Software Prototyping Infrastructure (S2PI) [Santiago Nunez-Corrales] 
\item CodeMeta [Alice Allen]
\item White paper on developing sustainable software [Sandra Gesing]
\item \todo{to confirm} Social Science of Scientific Software [Stuart Geiger]
\item Software Best Practices for Undergraduates [Jonah Miller]
\item Meaningful metrics for sustainable software [Emily Chen]
\item \todo{to confirm} Coordinating access to CI for research software [Mark Abraham]
\item Software engineering processes tailored for research software [Anshu Dubey]
\item Open research index [Dan]
\item \todo{to confirm} Letters of evaluation for computational scientists [Wolfgang Bangerth]
\end{itemize}

\input{wg_best_practices_sustainability}
\input{wg_prototyping}
\input{wg_codemeta}
\input{wg_best_practices_developing}
\input{wg_best_practices_undergrads}
\input{wg_metrics}
\input{wg_soft_eng}
\input{wg_open_research_index}

>>>>

\begin{itemize}
\item Verifying best practices \& metrics for sustainable research software [Ray Idaszak]
\item \todo{to confirm} Software Sustainability Alliance [Neil \& Jean]
\item Scientific Software Prototyping Infrastructure (S2PI) [Santiago Nunez-Corrales] 
\item CodeMeta [Alice Allen]
\item White paper on developing sustainable software [Sandra Gesing]
\item Social Science of Scientific Software [Stuart Geiger]
\item Software Best Practices for Undergraduates [Jonah Miller]
\item Meaningful metrics for sustainable software [Emily Chen]
\item \todo{to confirm} Coordinating access to CI for research software [Mark Abraham]
\item Software engineering processes tailored for research software [Anshu Dubey]
\item Open research index [Dan]
\item Letters of evaluation for computational scientists [Wolfgang Bangerth]
\end{itemize}

\input{wg_best_practices_sustainability}
\input{wg_prototyping}
\input{wg_codemeta}
\input{wg_best_practices_developing}
\input{wg_social}
\input{wg_best_practices_undergrads}
\input{wg_metrics}
\input{wg_soft_eng}
\input{wg_open_research_index}
\input{wg_letters}
